A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-17 papers/publication/paper-pollard.tex
EuroPar 2017 commit. Here goes nothing.

The behavior of PageRank is slightly different. As with SSSP and BFS, the GAP Benchmark Suite is the fastest but it also requires the fewest iterations.

We attempt to define similar stopping criteria for each system, but GraphMat executes until no vertices change rank; effectively its stopping criterion requires the $\infty$-norm be less than machine epsilon. This could account for the increased number of iterations. We adjusted the other systems to use $\sum_{k=1}^{n} |p_k^{(i)} - p_k^{(i-1)}| < \epsilon $ as the stopping criteria, where $i$ is the iteration and $n$ is the number of vertices. We use $\epsilon = 6 \times 10^{-8}$ because this value is approximately machine epsilon for a single precision floating-point number. The goal is to make the stopping criteria for all implementations as similar as possible.

>>>>

The behavior of PageRank is slightly different. As with SSSP and BFS, the GAP Benchmark Suite is the fastest but it also requires the fewest iterations. We attempt to define similar stopping criteria for each system, but GraphMat executes until no vertices change rank; effectively its stopping criterion requires the $\infty$-norm be less than machine epsilon. This could account for the increased number of iterations. We adjusted the other systems to use $\sum_{k=1}^{n} |p_k^{(i)} - p_k^{(i-1)}| < \epsilon $ as the stopping criterion, where $i$ is the iteration and $n$ is the number of vertices. We use $\epsilon = 6 \times 10^{-8}$ because this value is approximately machine epsilon for a single precision floating-point number. The goal is to make the stopping criteria for all implementations as similar as possible.
